Type Refinements for the Working Class

### 2015-11-11 paper.tex
More progress

\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{catchfilebetweentags}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{ifdraft}
\usepackage{ifthen}
\usepackage{mathtools}
\usepackage{proof}
\usepackage{scalerel}
\usepackage{setspace}
\usepackage{stmaryrd}
\usepackage{supertabular}
\usepackage{tikz-cd}
\usepackage{url}

@@

\newcommand\Refines[3]{\IMode{#1}\parallel \IMode{#2} \sqsubset \OMode{#3}}
\newcommand\GRefines[2]{\IMode{#1}\sqsubset\OMode{#2}}
\newcommand\RefinesCtx[2]{\IMode{#1}\sqsubset^\star\OMode{#2}}

@@

Fixing a signature $\Match{\Sigma}{\Pair{\Sorts}{\Operators}}$ in the abt
framework, we will define the notion of behavioral refinement by propounding
several judgments and their semantical explanations. We will require two
judgments, defined mutually: $\RefinesCtx{\Phi}{\Upsilon}$, which means that
$\Phi$ is a context which refines the symbol context $\Upsilon$ (presupposing
$\IsSymCtx{\Upsilon}$), and $\Refines{\Phi}{\phi}{\tau}$, which shall presuppose
$\RefinesCtx{\Phi}{\Upsilon}$ and $\IsSort{\tau}$).

@@

The second judgment is defined coinductively via the following meaning
explanation:
\begin{definition}[Refinement]
  To know $\Refines{\Phi}{\phi}{\tau}$ (presupposing
  $\RefinesCtx{\Phi}{\Upsilon}$ and $\IsSort{\tau}$) is to know, for any renaming
  $\Of{\varrho}{\Upsilon\hookrightarrow\OMode{\Upsilon'}}$, and for any $M, N$,
  what it means for $M$ and $N$ to be identified under $\phi$, supposing
  $\IsAbt{\cdot}{\Upsilon'}{\cdot}{M}{\tau}$ and
  $\IsAbt{\cdot}{\Upsilon'}{\cdot}{N}{\tau}$, requiring that if
  $\IMode{M}\sim_\phi\IMode{N}$ then $\IMode{N}\sim_\phi\IMode{M}$, and if
  $\IMode{M}\sim_\phi\IMode{N}$ and $\IMode{N}\sim_\phi\IMode{O}$, then
  $\IMode{M}\sim_\phi\IMode{O}$.
\end{definition}

@@

>>>>

\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{leftidx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{catchfilebetweentags}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{ifdraft}
\usepackage{ifthen}
\usepackage{mathtools}
\usepackage{proof}
\usepackage{scalerel}
\usepackage{setspace}
\usepackage{stmaryrd}
\usepackage{supertabular}
\usepackage{tikz-cd}
\usepackage{url}

@@

\newcommand\Refines[3]{\IMode{#1}\parallel \IMode{#2} \sqsubset \OMode{#3}}
\newcommand\GRefines[2]{\IMode{#1}\sqsubset\OMode{#2}}
\newcommand\RefinesCtx[2]{\IMode{#1}\sqsubset^\star\OMode{#2}}
\newcommand\EqRefines[4]{\IMode{#1}\parallel\IMode{#2}=\IMode{#3}\sqsubset\OMode{#4}}

\newcommand\HRefines[4]{\IMode{#1}\parallel\IMode{#2}\vDash\IMode{#3}\sqsubset\OMode{#4}}
\newcommand\HEqRefines[5]{\IMode{#1}\parallel\IMode{#2}\vDash\IMode{#3}=\IMode{#4}\sqsubset\OMode{#5}}
\newcommand\PRefinesCtx[3]{\IMode{#1}\parallel\IMode{#2}\sqsubset^\star\OMode{#3}}

\newcommand\RMemEq[4]{\IMode{#1}\parallel \IMode{#2}=\IMode{#3}\in \IMode{#4}}
\newcommand\HRMemEq[5]{\IMode{#1}\parallel \IMode{#2} \vDash \IMode{#3}=\IMode{#4}\in \IMode{#5}}

@@

Fixing a signature $\Match{\Sigma}{\Pair{\Sorts}{\Operators}}$ in the abt
framework, we will define the notion of behavioral refinement by propounding
several judgments and their semantical explanations.

\subsection{Parametric Refinement}

We will require two judgments, defined mutually: $\RefinesCtx{\Phi}{\Upsilon}$,
which means that $\Phi$ is a symbol context which refines the symbol context
$\Upsilon$ (presupposing $\IsSymCtx{\Upsilon}$), and parametric refinement
$\Refines{\Phi}{\phi}{\tau}$, which shall presuppose
$\RefinesCtx{\Phi}{\Upsilon}$ and $\IsSort{\tau}$).

@@

The second judgment is defined coinductively via the following meaning
explanation:
\begin{definition}[Parametric Refinement]
  To know $\Refines{\Phi}{\phi}{\tau}$ (presupposing
  $\RefinesCtx{\Phi}{\Upsilon}$ and $\IsSort{\tau}$) is to know, for any renaming
  $\Of{\varrho}{\Upsilon\hookrightarrow\OMode{\Upsilon'}}$, and for any $M, N$,
  what it means for $M$ and $N$ to be identified under $\phi$, supposing
  $\IsAbt{\cdot}{\Upsilon'}{\cdot}{M}{\tau}$ and
  $\IsAbt{\cdot}{\Upsilon'}{\cdot}{N}{\tau}$, requiring that if
  $\IMode{M}\sim^\rho_\phi\IMode{N}$ then $\IMode{N}\sim^\rho_\phi\IMode{M}$, and if
  $\IMode{M}\sim^\rho_\phi\IMode{N}$ and $\IMode{N}\sim^\rho_\phi\IMode{O}$, then
  $\IMode{M}\sim^\rho_\phi\IMode{O}$.
\end{definition}

@@

\subsubsection{Equality of parametric refinement}

Two refinements are equal when they denote the same PER. That is, will define
the refinement equality judgment $\EqRefines{\Phi}{\phi}{\psi}{\tau}$ as
follows, presupposing $\RefinesCtx{\Phi}{\Upsilon}$,
$\Refines{\Phi}{\phi}{\tau}$ and $\Refines{\Phi}{\psi}{\tau}$:
\begin{definition}
  To know $\EqRefines{\Phi}{\phi}{\psi}{\tau}$ is to know, for any substitution
  $\Of{\rho}{\Upsilon\hookrightarrow\OMode{\Upsilon'}}$, and for any $M, N$
  such that $\IsAbt{\cdot}{\Upsilon'}{\cdot}{M}{\tau}$ and
  $\IsAbt{\cdot}{\Upsilon'}{\cdot}{N}{\tau}$,
  $\IMode{M}\sim^\rho_\phi\IMode{N}$ if and only if
  $\IMode{M}\sim^\rho_\psi\IMode{N}$.
\end{definition}

\subsection{Parametric Equality}

The primary judgment concerning refinements is the parametric equality,
$\RMemEq{\Phi}{M}{N}{\phi}$, which presupposes $\RefinesCtx{\Phi}{\Upsilon}$,
$\Refines{\Phi}{\phi}{\tau}$, $\IsAbt{\cdot}{\Upsilon}{\cdot}{M}{\tau}$ and
$\IsAbt{\cdot}{\Upsilon}{\cdot}{N}{\tau}$. The meaning of this judgment is that
$M$ and $N$ are identified by $\phi$ at the identity renaming
$\Of{1}{\IMode{\Upsilon}\hookrightarrow\OMode{\Upsilon}}$:
\[
  \infer{
    \RMemEq{\Phi}{M}{N}{\phi}
  }{
    \IMode{M}\sim^1_\phi\IMode{N}
  }
\]

\subsection{Functional Refinement and Equality}

\newcommand\PRefinesCtxNil{\leftidx{^\parallel}{\!\!\sqsubset}{^\star_{\mathtt{nil}}}}
\newcommand\PRefinesCtxSnoc{\leftidx{^\parallel}{\!\!\sqsubset}{^\star_{\mathtt{snoc}}}}

Next, we define hypothetico-general (or \emph{functional}) refinement
$\HEqRefines{\Phi}{\Psi}{\phi}{\psi}{\tau}$ in terms of parametric refinement,
simultaneously with parametric context refinement
$\PRefinesCtx{\Phi}{\Psi}{\Gamma}$ and functional equality
$\HRMemEq{\Phi}{\Psi}{M}{N}{\phi}$. We will write
$\HRefines{\Phi}{\Psi}{\phi}{\tau}$ as a shorthand for
$\HEqRefines{\Phi}{\Psi}{\phi}{\phi}{\tau}$.

\newcommand\DefPRefinesCtxNil[1]{
  \infer[\PRefinesCtxNil]{
    \PRefinesCtx{#1}{\cdot}{\cdot}
  }{
  }
}
\newcommand\DefPRefinesCtxSnoc[6]{
  \infer[\PRefinesCtxSnoc]{
    \PRefinesCtx{#1}{#2,#3:#4}{#5,#3:#6}
  }{
    \PRefinesCtx{#1}{#2}{#5} &
    \HRefines{#1}{#2}{#4}{#6}
  }
}

Parametric context refinement $\PRefinesCtx{\Phi}{\Psi}{\Gamma}$ shall be
defined as follows, presupposing $\RefinesCtx{\Phi}{\Upsilon}$ and
$\IsVarCtx{\Gamma}$:
\begin{gather*}
  \DefPRefinesCtxNil{\Phi}\qquad
  \DefPRefinesCtxSnoc{\Phi}{\Psi}{x}{\phi}{\Gamma}{\tau}
\end{gather*}

Functional refinement $\HRefines{\Phi}{\Psi}{\phi}{\tau}$ presupposes
$\PRefinesCtx{\Phi}{\Psi}{\Gamma}$ and $\IsSort{\tau}$, and is explained by
induction on the evidence for its first presupposition.

\paragraph{Case} $\DefPRefinesCtxNil{\Phi}$.
\[
  \infer{
    \HRefines{\Phi}{\cdot}{\phi}{\tau}
  }{
    \Refines{\Phi}{\phi}{\tau}
  }
\]

\paragraph{Case} $\DefPRefinesCtxSnoc{\Phi}{\Psi}{x}{\psi}{\Gamma}{\sigma}$.
\begin{gather*}
  \infer{
    \HRefines{\Phi}{\Psi,x:\psi}{\phi}{\tau}
  }{
    \GenJ{y,z:\sigma}{
      \HypJ{
        \HEqRefines{\Phi}{\Psi}{\Subst{y}{x}{\phi}}{\Subst{z}{x}{\phi}}{\tau}
      }{
        \HRMemEq{\Phi}{\Psi}{y}{z}{\phi}
      }
    }
  }
\end{gather*}

%% Functional equality $\HRMemEq{\Phi}{\Psi}{M}{N}{\phi}$ is defined by
%% induction on the evidence for its presupposition
%% $\PRefinesCtx{\Phi}{\Psi}{\Gamma}$:
%% \begin{gather*}
%%   \infer{
%%     \HRMemEq{\Phi}{\cdot}{M}{N}{\phi}
%%   }{
%%     \RMemEq{\Phi}{M}{N}{\phi}
%%   }\qquad
%%   \infer{
%%     \HRMemEq{\Phi}{\Psi,x:\psi}{M}{N}{\phi}
%%   }{
%%  }
%%\end{gather*}

%%
%% \subsection{Parametric functional equality}
%%
%% Next, we will define the parametric hypothetico-general (or \emph{functional})
%% equality
%% $\IMode{\Phi}\parallel\IMode{\Psi}\vDash\IMode{M}=\IMode{N}\in\IMode{\phi}$
%% simultaneously with variable context well-formedness,
%% $\IMode{\Phi}\parallel\RefinesCtx{\Psi}{\Gamma}$.
